### 2012-10-23 2.tex
Writing on 1-4, especially edits on 3

\citet{Halle1962} and \citet{Chomsky1965} use two nonce words, \emph{blick} [blɪk] and \emph{bnick} [bnɪk], to illustrate that speakers internalize generalizations about possible and impossible words in their language. While \emph{blick} is unattested, but in some sense a ``possible'' word of English, \citeauthor{Chomsky1965} observe that speakers immediately recognize \emph{bnick} to be ill-formed, an impossible word, despite the fact that it is well-formed in other languages (e.g., Moroccan Arabic \emph{bniqa} `closet').

@@

\citet{Albright2003b} gathered wordlikeness judgements to serve as norms for a \emph{wug}-test. 87 items were presented to 24 undergraduate subjects, who rated each word on a seven-point Likert scale. The lowest point on the scale was labeled ``completely bizarre, impossible as an English word'', and that the highest point was labeled ``complete normal, would make a fine English word''.

@@

\citeauthor{Albright2009a} estimates bigram probabilities using the method of maximum likelihood over types in the lexicon. The variant of segmental bigrams used here computes probabilities with a simple type of smoothing in which the count of all possible bigrams (including those never observed) are incremented by one. This technique is known as Laplace, or ``add one'' smoothing. This has the desirable effect that no nonce word is ever assigned a zero probability, and produces a small increase in the correlation between the \citeauthor{Albright2003b} wordlikeness norms compared with the maximum likelihood estimate (Table \ref{albrightimproved}). For all three data sets, this model also consistenly outperforms positional probability models defined by \citet{Vitevitch2004} and \citet{Vaden2009}. 
Given this and the fact that these model scores are highly correlatd with bigram probability \citep[][54]{Vitevitch1997}, they are not considered further. The bigram model consistently performs well in all the evaluations, and has the highest Spearman correlation with the \citeauthor{Greenberg1964} and \citeauthor{Scholes1966} data, and is frequently second place model to the binary baseline elsewhere.

@@

The primary result is that no gradient model reliably exceeds the accuracy of the binary baseline. Despite this, there are relatively strong correlations between the binary baseline and these gradient models (see Table \ref{bcor}). However, the fact that the gradient models are generally outperformed by the binary baseline suggest that they do not reliably predict intermediate ratings. To quantify this, the following method was used to estimate the residual contribution of the three gradient models once gross phonotactic violations are taken into account. Instead of calculating rank correlations directly on the model scores as in Table \ref{cor}, the model scores are mapped to ranks with the additional constraint that all ``valid'' stimuli be ranked above all ``invalid'' stimuli. The resulting ranks are used to compute new correlation statistics. Finally, the binary baseline correlation is subtracted from this number, so that the resulting value is the amount of improvement derived from augmenting the binary model with gradience. These difference numbers are shown in Table \ref{controlled}. In most cases, including the gradient models on top of the binary baseline produces a worse correlation than is obtained with the binary baseline alone.

>>>>

\citet{Halle1962} and \citet{Chomsky1965} use two nonce words, \emph{blick} [blɪk] and \emph{bnick} [bnɪk], to illustrate that speakers internalize generalizations about possible and impossible words in their language. While \emph{blick} is unattested, but in some sense a ``possible'' word of English, \citeauthor{Chomsky1965} observe that speakers immediately recognize \emph{bnick} to be ill-formed, an impossible word, though it is well-formed in other languages (e.g., Moroccan Arabic \emph{bniqa} `closet').

@@

\citet{Albright2003b} gathered wordlikeness judgements to serve as norms for a \emph{wug}-test. 87 items were presented to 24 undergraduate subjects, who rated each word on a seven-point Likert scale. The lowest point on the scale was labeled ``completely bizarre, impossible as an English word'', and that the highest point was labeled ``completely normal, would make a fine English word''.

@@

\citeauthor{Albright2009a} estimates bigram probabilities using the method of maximum likelihood over types in the lexicon. The variant of segmental bigrams used here computes probabilities with a simple type of smoothing in which the count of all possible bigrams (including those never observed) are incremented by one. This technique is known as Laplace, or ``add one'' smoothing. This has the desirable effect that no nonce word is ever assigned a zero probability, and produces a small increase in the correlation between the \citeauthor{Albright2003b} wordlikeness norms compared with the maximum likelihood estimate (Table \ref{albrightimproved}). For all three data sets, this model also consistenly outperforms positional probability models defined by \citet{Vitevitch2004} and \citet{Vaden2009}; given that these model scores are highly correlatd with bigram probability \citep[][54]{Vitevitch1997}, they are not considered further. The bigram model consistently performs well in all the evaluations, and has the highest Spearman correlation with the \citeauthor{Greenberg1964} and \citeauthor{Scholes1966} data, and is frequently second place model to the binary baseline elsewhere.

@@

The primary result is that no gradient model reliably exceeds the accuracy of the binary baseline. Despite this, there are relatively strong correlations between the binary baseline and these gradient models (see Table \ref{bcor}). From the strong performance of the categorical model one can infer that the gradient models do not reliably predict intermediate ratings, or contrasts in ratings between words which are grouped together. To quantify this, the following method was used to estimate the residual contribution of the three gradient models once gross phonotactic violations are taken into account. Instead of calculating rank correlations directly on the model scores as in Table \ref{cor}, the model scores are mapped to ranks with the additional constraint that all ``valid'' stimuli be ranked above all ``invalid'' stimuli. The resulting ranks are used to compute new correlation statistics. Finally, the binary baseline correlation is subtracted from this number, so that the resulting value is the amount of improvement derived from augmenting the binary model with gradience. These difference numbers are shown in Table \ref{controlled}. In most cases, including the gradient models on top of the binary baseline produces a worse correlation than is obtained with the binary baseline alone.

### 2012-10-23 4.tex
Writing on 1-4, especially edits on 3

Finally, \citet[][176]{Pierrehumbert1994} observes ``a lack of clusters with identical first and third elements''. Here, this is operationalized in the same fashion as \textsc{Degemination}, by definining ``identity'' as consonants which share the same place and manner features, but which do not necessarily agree on voicing. Despite the fact that the corpus contains no exceptions to this generalization, these \textsc{ABA} clusters are not significantly less common than other triconsonantal and quadraconsonantal clusters.

>>>>

Finally, \citet[][176]{Pierrehumbert1994} observes ``a lack of clusters with identical first and third elements''. Here, this is operationalized in the same fashion as \textsc{Degemination}, by definining ``identity'' as consonants which share the same place and manner features, but which do not necessarily agree on voicing. Though the corpus contains no exceptions to this generalization, these \textsc{ABA} clusters are not significantly less common than other triconsonantal and quadraconsonantal clusters.

### 2012-10-23 pre.tex
Writing on 1-4, especially edits on 3

Similarly, theorists of lexical processing postulate that complex words are stored in memory to account for the facilitatory effect of whole word frequency on reaction times to complex words \citep[e.g.,][]{Alegre1999,Baayen1997a,Sereno1997}. But this effect of word frequency obtains regardless of whether or not whole word storage is postulated \citep{Taft2004b,LignosInPress}. Furthermore, in languages with rich agglutinative morphology, the role played by a whole word storage mechanism, should one be evidenced, would necessarily be quite marginal \citep{Anderson1988a,Hankamer1992,Chan2008}. According to one estimate, children acquiring American English hear 165,000 word tokens a week \citep{Swingley2007}. At that rate, it would take more than two months for a child to encounter the 1.5 milllion inflectional variants of a single verb in Archi \citep[467]{Kibrik1998},
%, cited in \citealt[122]{Bauer2001}), 
even if adult speech consisted of nothing but orderly recitation of the inflectional forms of this one verb, one after the other, without repetition.

>>>>

Similarly, theorists of lexical processing postulate that complex words are stored in memory to account for the facilitatory effect of whole word frequency on reaction times to complex words \citep[e.g.,][]{Alegre1999,Baayen1997b,Sereno1997}. But this effect of word frequency obtains regardless of whether or not whole word storage is postulated \citep{Taft2004b,LignosInPress}. Furthermore, in languages with rich agglutinative morphology, the role played by a whole word storage mechanism, should one be evidenced, would necessarily be quite marginal \citep{Anderson1988a,Hankamer1992,Chan2008}. According to one estimate, children acquiring American English hear 165,000 word tokens a week \citep{Swingley2007}. At that rate, it would take more than two months for a child to encounter the 1.5 milllion inflectional variants of a single verb in Archi \citep[467]{Kibrik1998},
%, cited in \citealt[122]{Bauer2001}), 
even if adult speech consisted of nothing but orderly recitation of the inflectional forms of this one verb, one after the other, without repetition.
